---
title: "Diss cleaning"
author: "SCL"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
library(pwr)      # pwr.f2.test
library(sjstats)  # design_effect
library(dplyr)
library(tibble)
library(purrr)
library(tidyverse)
library(janitor)
library(here)
library(psych)
library(car)
library(effectsize)
library(broom)
library(knitr)
library(kableExtra)
library(lattice)
library(nlme)
library(lubridate)
library(lme4)
library(lmerTest)
```

LOAD DATA

```{r data-load}
library(here)
data_path = here::here("Diss_full.csv")
diss.full =  read.csv(data_path)
```

LET'S START CLEANING

```{r}
#make all the columns lowercase to help with coding 
names(diss.full) = tolower(names(diss.full))
names(diss.full) =  iconv(names(diss.full), from = "", to = "UTF-8", sub = "")
names(diss.full) =  gsub("consent.*", "consent", names(diss.full))

```

Okay data is loaded. Now, we will clean it by the guidelines of the
pre-reg.

Participants will be excluded if they: 1) do not consent or 2) complete
the study in less than seven minutes or 3) exhibit no variability in
their responses (e.g., selecting all 5s or all 3s) across all Integrity
and likeability items, and 4) fail to complete the Integrity and
likeability ratings for at least one vignettes.

An attention check will be used to assess whether participants paid
attention during the experiment by requiring participants to select a
specific response to the question (i.e., “Select the option “somewhat
disagree” if you are paying attention.”). We will do an exploratory
analysis to determine test if excluding those who fail the attention
impacts the data.

```{r}
# Initial data count
initial_count =  nrow(diss.full)
print(initial_count)

# Clean recordeddate
diss.full$recordeddate =  str_squish(as.character(diss.full$recordeddate))
diss.full$created_date = mdy_hm(diss.full$recordeddate)

# Filters by cutoff date
cutoff_date =  as.Date("2026-01-27")
filtered_by_date = diss.full %>%
  filter(!is.na(created_date) & created_date >= cutoff_date)

count_by_date =  nrow(filtered_by_date)
print(count_by_date)

# Filter by consent
filtered_by_consent = filtered_by_date %>%
  filter(consent == "Yes, I consent")

count_by_consent =  nrow(filtered_by_consent)

# Filter by duration (exclude under 420 seconds)
filtered_by_duration = filtered_by_consent %>%
  filter(!is.na(duration..in.seconds.) & duration..in.seconds. >= 420)

count_by_duration = nrow(filtered_by_duration)

# Exclude participants under 18
filtered_by_age = filtered_by_duration %>%
  filter(is.na(age) | age >= 18)

count_by_age = nrow(filtered_by_age)


# Exclude no-variability: participants who gave identical responses across
# all Integrity and likeability items — uses apply() to avoid rowwise() issues
Integrity_like_cols = c("khon","ksin","keth","klike","kapp",
                    "shon","ssin","seth","slike","sapp",
                    "hhon","hsin","heth","hlike","happ",
                    "fhon","fsin","feth","flike","fapp",
                    "xhon","xsin","xeth","xlike","xapp",
                    "yhon","ysin","yeth","ylike","yapp")

tl_matrix = filtered_by_age %>%
  select(all_of(Integrity_like_cols)) %>%
  mutate(across(everything(), as.numeric))

has_variability = apply(tl_matrix, 1, function(row) n_distinct(na.omit(row)) > 1)
filtered_by_variability = filtered_by_age[has_variability, ]
count_by_variability = nrow(filtered_by_variability)

# Exclude attention check failures (attention1 == 2 is correct response)
filtered_by_attention = filtered_by_variability %>%
  filter(attention1 == 2)
count_by_attention = nrow(filtered_by_attention)
# Final count
final_count = nrow(filtered_by_age)

# Summary table
count_summary = data.frame(
  Step = c(
    "Initial",
    "After Date Filter",
    "After Consent Filter",
    "After Duration Filter",
    "After Age Filter",
    "Final"
  ),
  Count = c(
    initial_count,
    count_by_date,
    count_by_consent,
    count_by_duration,
    count_by_age,
    final_count
  )
)

print(count_summary)

# Print counts
cat("Total rows in diss.full:", initial_count, "\n")
cat("Rows after filtering by date:", count_by_date, "\n")
cat("Rows after filtering by consent:", count_by_consent, "\n")
cat("Rows after filtering by duration:", count_by_duration, "\n")
cat("Rows after excluding participants under 18:", count_by_age, "\n")
cat("Final rows:", final_count, "\n")
```

okay now we filter by ege

```{r}
attr_dat = filtered_by_age %>%
  select(
    responseid,
    minsmart, minbetter, mincreative, minrather, minshould, minregard, mintyp, minkeep, minget,
    modsmart, modbett, modcreat, modrath, modshou, modreg, modtyp, modkeep, modget,
    majsmart, majbet, majcreat, majrath, majshould, majreg, majtyp, majkeep, majget
  )
```

we need to pivot the data to be useable

```{r}
attr_long = attr_dat %>%
  pivot_longer(
    cols = -responseid,
    names_to = "raw_item",
    values_to = "choice_raw"
  )
```

Data has been pivoted so now we need to clean up some columns and make a
column for severity.

```{r}
attr_long = attr_long %>%
  mutate(
    severity = case_when(
      str_detect(raw_item, "^min") ~ "minor",
      str_detect(raw_item, "^mod") ~ "moderate",
      str_detect(raw_item, "^maj") ~ "major",
      TRUE ~ NA_character_
    ),
    item_stub = str_remove(raw_item, "^(min|mod|maj)"),
    attribute = case_when(
      item_stub %in% c("smart") ~ "smarter",
      item_stub %in% c("better", "bett") ~ "better_researcher",
      item_stub %in% c("creative", "creat") ~ "creative",
      item_stub %in% c("rather", "rath") ~ "rather_be",
      item_stub %in% c("should", "shou") ~ "should_be",
      item_stub %in% c("regard", "reg") ~ "celebrated",
      item_stub %in% c("typ") ~ "typical",
      item_stub %in% c("keep") ~ "job_security",
      item_stub %in% c("get") ~ "job_outcome",
      TRUE ~ NA_character_
    )
  )
```

Check to make sure it looks correct and get a count

```{r}
head(attr_long, 20)
table(attr_long$severity, useNA = "ifany")
table(attr_long$attribute, useNA = "ifany")
```

Okay i am working towards making a column that tells us researcher role
now...

```{r}
attr_long2 = attr_long %>%
  tidyr::crossing(researcher = c("investigator", "inspector"))
```

figure out how many rows for the data

```{r}
head(attr_long2, 20)
dim(attr_long)
dim(attr_long2)
```

assign values to researcher roles

```{r}
attr_long2 = attr_long2 %>%
  mutate(
    chosen = case_when(
      str_detect(choice_raw, "^reported researcher") & researcher == "investigator" ~ 1,
      str_detect(choice_raw, "^reporting researcher") & researcher == "inspector" ~ 1,
      str_detect(choice_raw, "^neither") ~ 0,
      TRUE ~ 0
    )
  )
```

Check to make sure it looks correct and get a count

```{r}
head(attr_long2, 20)
table(attr_long2$chosen, useNA = "ifany")
table(attr_long2$researcher, attr_long2$chosen)
```

This is where i start to lay out the model data set so i can use it for
analysis.

```{r}
attr_model_dat = attr_long2 %>%
  mutate(
    researcher_ec = if_else(researcher == "inspector", 1, -1),
    severity_num = case_when(
      severity == "minor" ~ -1,
      severity == "moderate" ~ 0,
      severity == "major" ~ 1
    ),
    responseid = factor(responseid),
    researcher = factor(researcher, levels = c("investigator", "inspector")),
    severity = factor(severity, levels = c("minor", "moderate", "major")),
    attribute = factor(
      attribute,
      levels = c(
        "smarter",
        "better_researcher",
        "creative",
        "rather_be",
        "should_be",
        "celebrated",
        "typical",
        "job_security",
        "job_outcome"
      )
    ),
    vignette_id = factor(severity)
  )
```

Lets make a summary table for each variable

```{r}
str(attr_model_dat)
table(attr_model_dat$researcher)
table(attr_model_dat$severity)
table(attr_model_dat$attribute)
table(attr_model_dat$researcher_ec)
table(attr_model_dat$severity_num)
```

RUN MODEL 1

```{r}
A1 = glmer(
  chosen ~ researcher_ec + attribute +
    (1 | responseid) + (1 | vignette_id),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa")
)
```

give me the results of that model

```{r}
# chosen = 0 (not selected), 1 (selected)
summary(A1)
```

RUN MODEL 2

```{r}
# A2 tests whether choice differs by severity, controlling for attribute
# chosen = 0 (not selected), 1 (selected)

A2 = glmer(
  chosen ~ attribute + severity_num +
    (1 | responseid),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(A2)
```

RUN MODEL 3

```{r}
# A3: Tests whether choice differs by BOTH researcher and severity,
# while controlling for attribute type

# DV: chosen (0 = not selected, 1 = selected)

A3 = glmer(
  chosen ~ researcher_ec + attribute + severity_num +
    (1 | responseid),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(A3)
```

RUN MODEL 4

```{r}
# A4: Tests whether the effect of researcher depends on severity,
# while controlling for attribute type

# DV: chosen (0 = not selected, 1 = selected)

A4 = glmer(
  chosen ~ researcher_ec * severity_num + attribute +
    (1 | responseid),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(A4)
```

Pivot the dataset

```{r}
attr_long = attr_dat %>%
  pivot_longer(
    cols = -responseid,
    names_to = "raw_item",
    values_to = "choice_raw"
  )
```

find the correct columns to attribute to the variables

```{r}
attr_long = attr_long %>%
  mutate(
    severity = case_when(
      str_detect(raw_item, "^min") ~ "minor",
      str_detect(raw_item, "^mod") ~ "moderate",
      str_detect(raw_item, "^maj") ~ "major",
      TRUE ~ NA_character_
    ),
    item_stub = str_remove(raw_item, "^(min|mod|maj)"),
    attribute = case_when(
      item_stub %in% c("smart") ~ "smarter",
      item_stub %in% c("better", "bett") ~ "better_researcher",
      item_stub %in% c("creative", "creat") ~ "creative",
      item_stub %in% c("rather", "rath") ~ "rather_be",
      item_stub %in% c("should", "shou") ~ "should_be",
      item_stub %in% c("regard", "reg") ~ "celebrated",
      item_stub %in% c("typ") ~ "typical",
      item_stub %in% c("keep") ~ "job_security",
      item_stub %in% c("get") ~ "job_outcome",
      TRUE ~ NA_character_
    )
  )
```

Check to make sure it looks correct and get a count

```{r}
head(attr_long, 20)
table(attr_long$severity, useNA = "ifany")
table(attr_long$attribute, useNA = "ifany")
```

set roles

```{r}
attr_long2 = attr_long %>%
  tidyr::crossing(researcher = c("investigator", "inspector"))
```

figure out how many rows for the data

```{r}
head(attr_long2, 20)
dim(attr_long)
dim(attr_long2)
```

find the correct columns and attruibute them to role type

```{r}
attr_long2 = attr_long2 %>%
  mutate(
    chosen = case_when(
      str_detect(choice_raw, "^reported researcher") & researcher == "investigator" ~ 1,
      str_detect(choice_raw, "^reporting researcher") & researcher == "inspector" ~ 1,
      str_detect(choice_raw, "^neither") ~ 0,
      TRUE ~ 0
    )
  )
```

Check to make sure it looks correct and get a count

```{r}
head(attr_long2, 20)
table(attr_long2$chosen, useNA = "ifany")
table(attr_long2$researcher, attr_long2$chosen)
```

set up the data for the models

```{r}
attr_model_dat = attr_long2 %>%
  mutate(
    researcher_ec = if_else(researcher == "inspector", 1, -1),
    severity_num = case_when(
      severity == "minor" ~ -1,
      severity == "moderate" ~ 0,
      severity == "major" ~ 1
    ),
    responseid = factor(responseid),
    researcher = factor(researcher, levels = c("investigator", "inspector")),
    severity = factor(severity, levels = c("minor", "moderate", "major")),
    attribute = factor(
      attribute,
      levels = c(
        "smarter",
        "better_researcher",
        "creative",
        "rather_be",
        "should_be",
        "celebrated",
        "typical",
        "job_security",
        "job_outcome"
      )
    ),
    vignette_id = factor(severity)
  )
```

create some model tables

```{r}
str(attr_model_dat)
table(attr_model_dat$researcher)
table(attr_model_dat$severity)
table(attr_model_dat$attribute)
table(attr_model_dat$researcher_ec)
table(attr_model_dat$severity_num)

```

Run our first model in the model build for hypo 1

```{r}

A1 = glmer(
  chosen ~ researcher_ec + attribute +
    (1 | responseid) + (1 | vignette_id),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa")
)
```

summarize our baseline

```{r}
# chosen = 0 (not selected), 1 (selected)
summary(A1)
```

run model two

```{r}
# A2 tests whether choice differs by severity, controlling for attribute
# chosen = 0 (not selected), 1 (selected)

A2 = glmer(
  chosen ~ attribute + severity_num +
    (1 | responseid),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(A2)
```

run model three

```{r}
# A3: Tests whether choice differs by BOTH researcher and severity,
# while controlling for attribute type

# DV: chosen (0 = not selected, 1 = selected)

A3 = glmer(
  chosen ~ researcher_ec + attribute + severity_num +
    (1 | responseid),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(A3)
```

run model four

```{r}
# A4: Tests whether the effect of researcher depends on severity,
# while controlling for attribute type

# DV: chosen (0 = not selected, 1 = selected)

A4 = glmer(
  chosen ~ researcher_ec * severity_num + attribute +
    (1 | responseid),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(A4)
```

# Integrity & LIKEABILITY ANALYSIS (RQ1, RQ2) + TRUENESS (RQ3)

Research Question 1: How is integrity influenced by role and QRP
severity? • Hypothesis 1a: Inspectors will be rated higher in integrity
than investigators. • Hypothesis 1b: The relative integrity of
inspectors versus investigators will increase as QRP severity increases.

Research Question 2: How is likeability influenced by role and QRP
severity? • Hypothesis 2a: Investigators will be rated more likable than
inspectors. • Hypothesis 2b: At low QRP severity, investigators will be
rated as more likeable than inspectors, but at high QRP severity,
inspectors will be rated as more likeable than investigators.

Research Question 3: Is the perceived trueness of the finding influenced
by QRP severity? • Hypothesis 3: Perceived trueness will decrease as QRP
severity increases.

Research Questions 1–2: Integrity and Likeability Step-up MLMs will test
Role, Severity, and Role × Severity interaction:

Model 1: Integrity/Likeabilityijk = γ000 + γ100 (Researcherj) + ν0k +
μ0jk + εijk Model 2: Integrity/Likeabilityijk = γ000 + γ010
(Severityk) + ν0k + μ0k + εijk Model 3: Integrity/Likeabilityijk =
γ000 + γ100 (Researcherj) + γ010 (Severityk) + ν0k + μ0jk + εijk Model
4: Integrity/Likeabilityijk = γ000 + γ100 (Researcherj) + γ010
(Severityk) + γ110(Researcherj × Severityk) + ν0k + μ0jk + εijk

Research Question 3: Trueness of Findings Model FT1: Truenessijk= γ000 +
γ010 (Severityk) + ν0k + μ0j + εijk

## STEP 1: Build the long-format Integrity/likeability/trueness dataset

```{r build-Integrity-long}
# Vignette metadata
# Each vignette pair: investigator (inv) and inspector (insp)
# Severity:minor = vignette K/S, moderate = H/F, major = X/Y
# Integrity items: hon, sin, eth  (honest, sincere, ethical)
# Likeability: like, app (likeable, approachable)
# Trueness (conf): investigator only, 1 item per vignette

vignette_map = list(
  list(vig_id = "minor",    role = "investigator",
       hon = "khon", sin = "ksin",  eth = "keth",
       like = "klike",  app = "kapp",  conf = "kcon"),
  list(vig_id = "minor",    role = "inspector",
       hon = "shon",    sin = "ssin",  eth = "seth",
       like = "slike",  app = "sapp",  conf = NA),
  list(vig_id = "moderate", role = "investigator",
       hon = "hhon",    sin = "hsin",  eth = "heth",
       like = "hlike",  app = "happ",  conf = "hcon"),
  list(vig_id = "moderate", role = "inspector",
       hon = "fhon",    sin = "fsin",  eth = "feth",
       like = "flike",  app = "fapp",  conf = NA),
  list(vig_id = "major",    role = "investigator",
       hon = "xhon",   sin = "xsin",  eth = "xeth",
       like = "xlike",  app = "xapp",  conf = "xcon"),
  list(vig_id = "major",    role = "inspector",
       hon = "yhon",    sin = "ysin",  eth = "yeth",
       like = "ylike",  app = "yapp",  conf = NA)
)

#Helper: extract numeric value from labelled string
parse_num = function(x) as.numeric(str_extract(as.character(x), "^\\d"))

#Build one row per participant × vignette × role
tl_rows = bind_rows(lapply(vignette_map, function(v) {
  filtered_by_age %>%                          # use cleaned dataset
    transmute(
      responseid,
      vig_id   = v$vig_id,
      role     = v$role,
      hon_raw  = parse_num(.data[[v$hon]]),
      sin_raw  = parse_num(.data[[v$sin]]),
      eth_raw  = parse_num(.data[[v$eth]]),
      like_raw = parse_num(.data[[v$like]]),
      app_raw  = parse_num(.data[[v$app]]),
      conf_raw = if (!is.na(v$conf)) parse_num(.data[[v$conf]]) else NA_real_
    )
}))

#Composites & factors
tl_dat = tl_rows %>%
  mutate(
    Integrity      = rowMeans(cbind(hon_raw, sin_raw, eth_raw), na.rm = TRUE),
    likeability = rowMeans(cbind(like_raw, app_raw), na.rm = TRUE),
    severity   = factor(vig_id,   levels = c("minor", "moderate", "major")),
    role       = factor(role,     levels = c("investigator", "inspector")),
    responseid = factor(responseid),
    # effect-coded predictors
    role_ec    = if_else(role == "inspector", 1, -1),
    severity_num = case_when(
      severity == "minor"    ~ -1,
      severity == "moderate" ~  0,
      severity == "major"    ~  1
    )
  )

glimpse(tl_dat)
```

Check structure and counts

```{r tl-checks}
table(tl_dat$role, tl_dat$severity)

# Quick descriptives
tl_dat %>%
  group_by(role, severity) %>%
  summarise(
    n          = sum(!is.na(Integrity)),
    Integrity_M    = round(mean(Integrity, na.rm = TRUE), 2),
    Integrity_SD   = round(sd(Integrity,   na.rm = TRUE), 2),
    like_M     = round(mean(likeability, na.rm = TRUE), 2),
    like_SD    = round(sd(likeability,   na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  kable(caption = "Descriptives: Integrity & Likeability by Role × Severity") %>%
  kable_styling()
```

## STEP 2: Reliability & validation checks

```{r reliability}
library(psych)

#Integrity alpha per role × severity (using the 3 items)
Integrity_items_inv = filtered_by_age %>%
  transmute(
    min_hon = parse_num(khon), min_sin = parse_num(ksin),   min_eth = parse_num(keth),
    mod_hon = parse_num(hhon),    mod_sin = parse_num(hsin),   mod_eth = parse_num(heth),
    maj_hon = parse_num(xhon),   maj_sin = parse_num(xsin),   maj_eth = parse_num(xeth)
  )

Integrity_items_insp = filtered_by_age %>%
  transmute(
    min_hon = parse_num(shon),  min_sin = parse_num(ssin),  min_eth = parse_num(seth),
    mod_hon = parse_num(fhon),  mod_sin = parse_num(fsin),  mod_eth = parse_num(feth),
    maj_hon = parse_num(yhon),  maj_sin = parse_num(ysin),  maj_eth = parse_num(yeth)
  )

psych::alpha(Integrity_items_inv,  check.keys = TRUE)$total %>% select(raw_alpha, std.alpha) %>% print()

psych::alpha(Integrity_items_insp, check.keys = TRUE)$total %>% select(raw_alpha, std.alpha) %>% print()

#Likeability alpha
like_items_inv = filtered_by_age %>%
  transmute(
    min_like = parse_num(klike), min_app = parse_num(kapp),
    mod_like = parse_num(hlike), mod_app = parse_num(happ),
    maj_like = parse_num(xlike), maj_app = parse_num(xapp)
  )

like_items_insp = filtered_by_age %>%
  transmute(
    min_like = parse_num(slike), min_app = parse_num(sapp),
    mod_like = parse_num(flike), mod_app = parse_num(fapp),
    maj_like = parse_num(ylike), maj_app = parse_num(yapp)
  )

psych::alpha(like_items_inv,  check.keys = TRUE)$total %>% select(raw_alpha, std.alpha) %>% print()

psych::alpha(like_items_insp, check.keys = TRUE)$total %>% select(raw_alpha, std.alpha) %>% print()

#Inter-composite correlation
cor.test(tl_dat$Integrity, tl_dat$likeability, use = "complete.obs") %>% tidy() %>% print()
```

## STEP 3: Null models (Model 0) — ICC partitioning

```{r null-models}
library(lme4)
library(lmerTest)

#Integrity null model
M0_Integrity = lmer(
  Integrity ~ 1 + (1 | responseid) + (1 | severity),
  data = tl_dat,
  REML = TRUE
)
summary(M0_Integrity)

# ICC: proportion of variance at each level
vc_Integrity = as.data.frame(VarCorr(M0_Integrity))
icc_participant_Integrity = vc_Integrity$vcov[vc_Integrity$grp == "responseid"] / sum(vc_Integrity$vcov)
icc_vignette_Integrity    = vc_Integrity$vcov[vc_Integrity$grp == "severity"]   / sum(vc_Integrity$vcov)

print(paste("Integrity ICC (participant):", round(icc_participant_Integrity, 3)))
print(paste("Integrity ICC (vignette):",    round(icc_vignette_Integrity, 3)))

#Likeability null model
M0_like = lmer(
  likeability ~ 1 + (1 | responseid) + (1 | severity),
  data = tl_dat,
  REML = TRUE
)
summary(M0_like)

vc_like = as.data.frame(VarCorr(M0_like))
icc_participant_like = vc_like$vcov[vc_like$grp == "responseid"] / sum(vc_like$vcov)
icc_vignette_like    = vc_like$vcov[vc_like$grp == "severity"]   / sum(vc_like$vcov)

print(paste("Likeability ICC (participant):", round(icc_participant_like, 3)))
print(paste("Likeability ICC (vignette):",    round(icc_vignette_like, 3)))
```

## STEP 4: RQ1 — Integrity models (H1a: main effect of role; H1b: role × severity)

```{r Integrity-models}
# Model 1: Role only (H1a)
T1 = lmer(
  Integrity ~ role_ec + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 2: Severity only
T2 = lmer(
  Integrity ~ severity_num + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 3: Role + Severity (additive)
T3 = lmer(
  Integrity ~ role_ec + severity_num + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 4: Role × Severity interaction (H1b)
T4 = lmer(
  Integrity ~ role_ec * severity_num + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

#Model comparison
anova(T1, T2, T3, T4)

# Summaries
summary(T1)
summary(T2)
summary(T3)
summary(T4)
```

RANDOM SLOPE TESTING — per prereg: "random slopes for within-participant
predictors where possible." Role and severity are both within-participant
(fully crossed design), so we test maximal structure first and step down
only if models fail to converge or are singular.

```{r Integrity-slope-testing}
# Maximal: random slopes for role AND severity (plus their interaction) by participant
T4_max1 = lmer(
  Integrity ~ role_ec * severity_num + (1 + role_ec * severity_num | responseid),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)
isSingular(T4_max1)

# Step down: drop interaction slope, keep both main slopes
T4_max2 = lmer(
  Integrity ~ role_ec * severity_num + (1 + role_ec + severity_num | responseid),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)
isSingular(T4_max2)

# Step down further: keep only role slope (your key H1a/H1b predictor)
T4_max3 = lmer(
  Integrity ~ role_ec * severity_num + (1 + role_ec | responseid),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)
isSingular(T4_max3)
summary(T4_max1)
summary(T4_max2)
summary(T4_max3)

```

Planned contrasts: inspectors vs investigators at each severity level
(Bonferroni α = .001)

```{r Integrity-contrasts}
library(emmeans)

emm_Integrity = emmeans(T4, ~ role_ec | severity_num,
                     at = list(severity_num = c(-1, 0, 1)))

# Recode for readable output
emm_Integrity_role = emmeans(T4, pairwise ~ role_ec | severity_num,
                           at = list(severity_num = c(-1, 0, 1)),
                           adjust = "bonferroni")
summary(emm_Integrity_role$contrasts)

# Effect sizes (Cohen's d)
eff_size(emm_Integrity, sigma = sigma(T4), edf = df.residual(T4))
```

Plot Role × Severity for Integrity

```{r Integrity-plot}
emm_Integrity_df = as.data.frame(emmeans(T4, ~ role_ec * severity_num,
                                       at = list(severity_num = c(-1, 0, 1))))
emm_Integrity_df = emm_Integrity_df %>%
  mutate(
    Role     = if_else(role_ec == 1, "Inspector", "Investigator"),
    Severity = factor(severity_num, levels = c(-1, 0, 1),
                      labels = c("Minor", "Moderate", "Major"))
  )

ggplot(emm_Integrity_df, aes(x = Severity, y = emmean, color = Role, group = Role)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.15) +
  scale_color_manual(values = c("Inspector" = "#2196F3", "Investigator" = "#E53935")) +
  labs(title = "RQ1. Integrity",
       y = "Integrity (EMM)", x = "QRP Severity") +
  theme_minimal(base_size = 13) +
  coord_cartesian(ylim = c(1, 5))
```

## STEP 5: RQ2 — Likeability models (H2a: main effect of role; H2b: role × severity)

Research Question 2: How is likeability influenced by role and QRP
severity? • Hypothesis 2a: Investigators will be rated more likable than
inspectors. • Hypothesis 2b: At low QRP severity, investigators will be
rated as more likeable than inspectors, but at high QRP severity,
inspectors will be rated as more likeable than investigators.

Research Questions 1–2: Integrity and Likeability Step-up MLMs will test
Role, Severity, and Role × Severity interaction:

Model 1: Integrity/Likeabilityijk = γ000 + γ100 (Researcherj) + ν0k +
μ0jk + εijk Model 2: Integrity/Likeabilityijk = γ000 + γ010
(Severityk) + ν0k + μ0k + εijk Model 3: Integrity/Likeabilityijk =
γ000 + γ100 (Researcherj) + γ010 (Severityk) + ν0k + μ0jk + εijk Model
4: Integrity/Likeabilityijk = γ000 + γ100 (Researcherj) + γ010
(Severityk) + γ110(Researcherj × Severityk) + ν0k + μ0jk + εijk

```{r likeability-models}
# Model 1: Role only (H2a)
L1 = lmer(
  likeability ~ role_ec + (1 | responseid), 
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 2: Severity only
L2 = lmer(
  likeability ~ severity_num + (1 | responseid),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 3: Role + Severity (additive)
L3 = lmer(
  likeability ~ role_ec + severity_num + (1 | responseid),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 4: Role × Severity interaction (H2b)
L4 = lmer(
  likeability ~ role_ec * severity_num + (1 | responseid),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# model comparison
anova(L1, L2, L3, L4)

summary(L1)
summary(L2)
summary(L3)
summary(L4)
```

Random slope testing for likeability — same logic as Integrity above.

```{r likeability-slope-testing}
L4_max1 = lmer(
  likeability ~ role_ec * severity_num + (1 + role_ec * severity_num | responseid),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)
isSingular(L4_max1)

L4_max2 = lmer(
  likeability ~ role_ec * severity_num + (1 + role_ec + severity_num | responseid),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)
isSingular(L4_max2)

L4_max3 = lmer(
  likeability ~ role_ec * severity_num + (1 + role_ec | responseid),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)
isSingular(L4_max3)

summary(L4_max1)
summary(L4_max2)
summary(L4_max3)

# Use whichever is the most complex non-singular model as the structure
# for L1-L4 above; if all are singular, the intercept-only structure
# already used is justified and should be cited as such.
```

Planned contrasts: Bonferroni α = .001

```{r likeability-contrasts}
emm_like_role = emmeans(L4, pairwise ~ role_ec | severity_num,
                          at = list(severity_num = c(-1, 0, 1)),
                          adjust = "bonferroni")
summary(emm_like_role$contrasts)

eff_size(emmeans(L4, ~ role_ec | severity_num,
                  at = list(severity_num = c(-1, 0, 1))),
         sigma = sigma(L4), edf = df.residual(L4))
```

Plot Role × Severity for likeability

```{r like-plot}
emm_like_df = as.data.frame(emmeans(L4, ~ role_ec * severity_num,
                                      at = list(severity_num = c(-1, 0, 1)))) %>%
  mutate(
    Role     = if_else(role_ec == 1, "Inspector", "Investigator"),
    Severity = factor(severity_num, levels = c(-1, 0, 1),
                      labels = c("Minor", "Moderate", "Major"))
  )

ggplot(emm_like_df, aes(x = Severity, y = emmean, color = Role, group = Role)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.15) +
  scale_color_manual(values = c("Inspector" = "#2196F3", "Investigator" = "#E53935")) +
  labs(title = "Likeability",
       y = "Likeability(EMM)", x = "QRP Severity") +
  theme_minimal(base_size = 13) +
  coord_cartesian(ylim = c(1, 5))
```

## STEP 6: RQ3 — Perceived Trueness of the Finding (H3: severity → trueness)

Research Question 3: Trueness of Findings Model FT1: Truenessijk= γ000 +
γ010 (Severityk) + ν0k + μ0j + εijk

```{r trueness-data}
# Trueness is only for investigators, one item per vignette
trueness_dat = filtered_by_age %>%
  transmute(
    responseid,
    minor    = parse_num(kcon),
    moderate = parse_num(hcon),
    major    = parse_num(xcon)
  ) %>%
  pivot_longer(
    cols      = c(minor, moderate, major),
    names_to  = "severity",
    values_to = "trueness"
  ) %>%
  mutate(
    severity     = factor(severity, levels = c("minor", "moderate", "major")),
    severity_num = case_when(
      severity == "minor"    ~ -1,
      severity == "moderate" ~  0,
      severity == "major"    ~  1
    ),
    responseid = factor(responseid),
    trueness_c = trueness - 3
  )

# Descriptives
trueness_dat %>%
  group_by(severity) %>%
  summarise(
    n  = sum(!is.na(trueness)),
    M  = round(mean(trueness, na.rm = TRUE), 2),
    SD = round(sd(trueness,   na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  kable(caption = "Trueness Descriptives by QRP Severity") %>%
  kable_styling()
```

Model FT1: Trueness \~ Severity (H3)

```{r trueness-model}
FT1 = lmer(
  trueness_c ~ severity_num + (1 | responseid) + (1 | severity),
  data    = trueness_dat,
  REML    = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(FT1)
isSingular(FT1)

# Planned contrasts across severity levels
emm_trueness = emmeans(FT1, pairwise ~ severity_num,
                         at     = list(severity_num = c(-1, 0, 1)),
                         adjust = "bonferroni")
summary(emm_trueness$contrasts)

eff_size(emmeans(FT1, ~ severity_num, at = list(severity_num = c(-1, 0, 1))),
         sigma = sigma(FT1), edf = df.residual(FT1))
```

Plot trueness by severity

```{r trueness-plot}
emm_true_df = as.data.frame(
  emmeans(FT1, ~ severity_num, at = list(severity_num = c(-1, 0, 1)))
) %>%
  mutate(Severity = factor(severity_num, levels = c(-1, 0, 1),
                            labels = c("Minor", "Moderate", "Major")))

ggplot(emm_true_df, aes(x = Severity, y = emmean, group = 1)) +
  geom_line(linewidth = 2, color = "#7B1FA2") +
  geom_point(size = 5, color = "#7B1FA2") +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.20,
                color = "#7B1FA2") +
  labs(title = "Perceived Trueness of Finding by QRP Severity",
       y = "Trueness (EMM)", x = "QRP Severity") +
  theme_minimal(base_size = 15) +
  coord_cartesian(ylim = c(-2, 2))
```

------------------------------------------------------------------------

## STEP 7: Robustness checks — demographic covariates

```{r robustness-demographics}
# Attach demographics to tl_dat
demo_dat = filtered_by_age %>%
  transmute(
    responseid = responseid,
    gender     = factor(`gender.identity`),
    political  = factor(political, levels = c(
      "Strongly Liberal", "Liberal", "Lean Liberal",
      "Centrist",
      "Lean Conservative", "Conservative", "Strongly Conservative"
    )),
    religion   = factor(religion)
  )

tl_robust = tl_dat %>%
  mutate(responseid = as.character(responseid)) %>%
  left_join(demo_dat, by = "responseid") %>%
  mutate(responseid = factor(responseid))


# Integrity robustness model (Model 4 + demographics)
T4_robust = lmer(
  Integrity ~ role_ec * severity_num + gender + political + religion +
    (1 | responseid) + (1 | severity),
  data    = tl_robust,
  REML    = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

L4_robust = lmer(
  likeability ~ role_ec * severity_num + gender + political + religion +
    (1 | responseid) + (1 | severity),
  data    = tl_robust,
  REML    = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)


summary(L4_robust)

# Compare role_ec * severity_num effect with and without demographics
summary(T4_robust)
summary(L4_robust)

# Check if the interaction term stays significant in both
fixef(T4)[["role_ec:severity_num"]]
fixef(T4_robust)[["role_ec:severity_num"]]

fixef(L4)[["role_ec:severity_num"]]
fixef(L4_robust)[["role_ec:severity_num"]]
```

# ── APA Model Comparison Tables ──────────────────────────────────────────────

```{r apa-tables}

# Helper: extract fixed effects from a model into a clean data frame
fe_table = function(model) {
  cf = summary(model)$coefficients
  ci = confint(model, method = "Wald")
  ci = ci[rownames(cf), ]
  data.frame(
    Parameter = rownames(cf),
    b         = round(cf[, "Estimate"], 2),
    SE        = round(cf[, "Std. Error"], 2),
    CI_low    = round(ci[, 1], 2),
    CI_high   = round(ci[, 2], 2),
    t         = round(cf[, "t value"], 2),
    p         = ifelse(cf[, "Pr(>|t|)"] < .001, "< .001",
                       formatC(cf[, "Pr(>|t|)"], digits = 3, format = "f"))
  )
}

# Helper: APA-friendly term labels
relabel = function(df) {
  df$Parameter = dplyr::recode(df$Parameter,
    "(Intercept)"          = "Intercept",
    "role_ec"              = "Role",
    "severity_num"         = "QRP Severity",
    "role_ec:severity_num" = "Role × QRP Severity"
  )
  df
}

# Helper: model fit summary table
fit_table = function(model_list, model_names) {
  do.call(rbind, lapply(seq_along(model_list), function(i) {
    m = model_list[[i]]
    data.frame(
      Model  = model_names[i],
      AIC    = round(AIC(m), 1),
      BIC    = round(BIC(m), 1),
      logLik = round(as.numeric(logLik(m)), 1)
    )
  }))
}

# ── TABLE 1: Integrity model fit ──────────────────────────────────────────────
fit_table(
  list(T1, T2, T3, T4),
  c("M1: Role", "M2: Severity", "M3: Role + Severity", "M4: Role × Severity")
) %>%
  kable(caption = "Table 1. Model Fit Indices for Step-Up Integrity Models",
        align = "lrrr") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "condensed") %>%
  footnote(general = "Lower AIC/BIC indicates better model fit.")

# ── TABLE 2: Integrity fixed effects (Model 4) ────────────────────────────────
fe_table(T4) %>%
  relabel() %>%
  mutate(`95% CI` = paste0("[", CI_low, ", ", CI_high, "]")) %>%
  select(Parameter, b, SE, `95% CI`, t, p) %>%
  kable(caption = "Table 2. Fixed Effects for Integrity Model 4 (Role × QRP Severity)",
        col.names = c("Parameter", "b", "SE", "95% CI", "t", "p"),
        align = "lrrrrr") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "condensed") %>%
  footnote(general = "Role: inspector = 1, investigator = −1. QRP Severity: minor = −1, moderate = 0, major = 1.")

# ── TABLE 3: Likeability model fit ───────────────────────────────────────
fit_table(
  list(L1, L2, L3, L4),
  c("M1: Role", "M2: Severity", "M3: Role + Severity", "M4: Role × Severity")
) %>%
  kable(caption = "Table 3. Model Fit Indices for Step-Up Likeability Models",
        align = "lrrr") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "condensed") %>%
  footnote(general = "Lower AIC/BIC indicates better model fit.")

# ── TABLE 4: Likeability fixed effects (Model 4) ─────────────────────────
fe_table(L4) %>%
  relabel() %>%
  mutate(`95% CI` = paste0("[", CI_low, ", ", CI_high, "]")) %>%
  select(Parameter, b, SE, `95% CI`, t, p) %>%
  kable(caption = "Table 4. Fixed Effects for Likeability Model 4 (Role × QRP Severity)",
        col.names = c("Parameter", "b", "SE", "95% CI", "t", "p"),
        align = "lrrrrr") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "condensed") %>%
  footnote(general = "Role: inspector = 1, investigator = −1. QRP Severity: minor = −1, moderate = 0, major = 1.")

# ── TABLE 5: Trueness fixed effects (FT1) ────────────────────────────────
fe_table(FT1) %>%
  relabel() %>%
  mutate(`95% CI` = paste0("[", CI_low, ", ", CI_high, "]")) %>%
  select(Parameter, b, SE, `95% CI`, t, p) %>%
  kable(caption = "Table 5. Fixed Effects for Trueness Model FT1",
        col.names = c("Parameter", "b", "SE", "95% CI", "t", "p"),
        align = "lrrrrr") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "condensed") %>%
  footnote(general = "Trueness centered at 3 (neutral midpoint). QRP Severity: minor = −1, moderate = 0, major = 1.")
```

------------------------------------------------------------------------

## APA Step-Up Model Tables (side-by-side format)

```{r apa-stepup-tables}
get_fe = function(model) {
  cf = summary(model)$coefficients
  list(
    b  = setNames(round(cf[,"Estimate"], 2),   rownames(cf)),
    se = setNames(round(cf[,"Std. Error"], 2), rownames(cf)),
    p  = setNames(cf[,"Pr(>|t|)"],             rownames(cf))
  )
}

fmt_p = function(p) {
  if (is.na(p)) return("")
  stars = ifelse(p < .001, "***", ifelse(p < .01, "**", ifelse(p < .05, "*", "")))
  paste0(formatC(p, digits = 3, format = "f"), stars)
}

cell = function(fe, term) {
  if (!term %in% names(fe$b)) return(c("", "", ""))
  c(as.character(fe$b[term]), as.character(fe$se[term]), fmt_p(fe$p[term]))
}
get_re = function(model) {
  vc = as.data.frame(lme4::VarCorr(model))
  setNames(round(vc$sdcor^2, 3), vc$grp)
}

get_icc = function(model) {
  vc = as.data.frame(lme4::VarCorr(model))
  total = sum(vc$vcov)
  setNames(round(vc$vcov / total, 3), vc$grp)
}

make_stepup_table = function(m0, m1, m2, m3, m4, caption_text, footnote_text) {

  models   = list(m0, m1, m2, m3, m4)
  fe_list  = lapply(models, get_fe)
  re_list  = lapply(models, get_re)
  icc_list = lapply(models, get_icc)

  term_labels = c(
    "(Intercept)"          = "Intercept",
    "role_ec"              = "Role",
    "severity_num"         = "QRP Severity",
    "role_ec:severity_num" = "Role × QRP Severity"
  )

  rows = lapply(names(term_labels), function(term) {
    cells = do.call(cbind, lapply(fe_list, function(fe) cell(fe, term)))
    data.frame(
      Parameter = term_labels[term],
      M0_b = cells[1,1], M0_se = cells[2,1], M0_p = cells[3,1],
      M1_b = cells[1,2], M1_se = cells[2,2], M1_p = cells[3,2],
      M2_b = cells[1,3], M2_se = cells[2,3], M2_p = cells[3,3],
      M3_b = cells[1,4], M3_se = cells[2,4], M3_p = cells[3,4],
      M4_b = cells[1,5], M4_se = cells[2,5], M4_p = cells[3,5],
      stringsAsFactors = FALSE
    )
  })
  fe_df = do.call(rbind, rows)

  re_grps = c("responseid" = "Participant variance",
               "severity"   = "Vignette variance",
               "Residual"   = "Residual variance")

  re_rows = lapply(names(re_grps), function(grp) {
    vals = sapply(re_list, function(re) {
      if (grp %in% names(re)) as.character(re[grp]) else "—"
    })
    data.frame(
      Parameter = re_grps[grp],
      M0_b = vals[1], M0_se = "", M0_p = "",
      M1_b = vals[2], M1_se = "", M1_p = "",
      M2_b = vals[3], M2_se = "", M2_p = "",
      M3_b = vals[4], M3_se = "", M3_p = "",
      M4_b = vals[5], M4_se = "", M4_p = "",
      stringsAsFactors = FALSE
    )
  })
  re_df = do.call(rbind, re_rows)

  icc_rows = lapply(names(re_grps)[1:2], function(grp) {
    vals = sapply(icc_list, function(ic) {
      if (grp %in% names(ic)) as.character(ic[grp]) else "—"
    })
    data.frame(
      Parameter = paste("ICC:", re_grps[grp]),
      M0_b = vals[1], M0_se = "", M0_p = "",
      M1_b = vals[2], M1_se = "", M1_p = "",
      M2_b = vals[3], M2_se = "", M2_p = "",
      M3_b = vals[4], M3_se = "", M3_p = "",
      M4_b = vals[5], M4_se = "", M4_p = "",
      stringsAsFactors = FALSE
    )
  })
  icc_df = do.call(rbind, icc_rows)

  fit_vals = sapply(models, function(m) c(round(AIC(m),1), round(BIC(m),1)))
  fit_df = data.frame(
    Parameter = c("AIC", "BIC"),
    M0_b = as.character(fit_vals[,1]), M0_se = "", M0_p = "",
    M1_b = as.character(fit_vals[,2]), M1_se = "", M1_p = "",
    M2_b = as.character(fit_vals[,3]), M2_se = "", M2_p = "",
    M3_b = as.character(fit_vals[,4]), M3_se = "", M3_p = "",
    M4_b = as.character(fit_vals[,5]), M4_se = "", M4_p = "",
    stringsAsFactors = FALSE
  )

  full_df = rbind(fe_df, re_df, icc_df, fit_df)

  full_df %>%
    kable(
      caption = caption_text,
      col.names = c("Parameter",
                    "b", "SE", "p",
                    "b", "SE", "p",
                    "b", "SE", "p",
                    "b", "SE", "p",
                    "b", "SE", "p"),
      align = c("l", rep("r", 15))
    ) %>%
    kable_styling(full_width = TRUE, font_size = 11,
                  bootstrap_options = c("condensed", "bordered")) %>%
    add_header_above(c(" " = 2,
                       "Model 0" = 3, "Model 1" = 3,
                       "Model 2" = 3, "Model 3" = 3,
                       "Model 4" = 3)) %>%
    footnote(general = footnote_text,
             general_title = "Note.",
             footnote_as_chunk = TRUE)
}

make_stepup_table(
  m0 = M0_Integrity, m1 = T1, m2 = T2, m3 = T3, m4 = T4,
  caption_text = "Table 1. Step-Up MLM Results for Integrity (Integrity) Ratings",
  footnote_text = "Role effect-coded: inspector = 1, investigator = −1. QRP Severity: minor = −1, moderate = 0, major = 1. * p < .05. ** p < .01. *** p < .001."
)
# ── LIKEABILITY TABLE
make_stepup_table(
  m0 = M0_like, m1 = L1, m2 = L2, m3 = L3, m4 = L4,
  caption_text = "Table 2. Step-Up MLM Results for Likeability Ratings",
  footnote_text = "Role effect-coded: inspector = 1, investigator = −1. QRP Severity: minor = −1, moderate = 0, major = 1. * p < .05. ** p < .01. *** p < .001."
)
```

```{r}
# ── TRUENESS TABLE (single model) ─────────────────────────────────────────────
fe_ft1 = get_fe(FT1)
re_ft1 = get_re(FT1)
icc_ft1 = get_icc(FT1)

data.frame(
  Parameter = c("Intercept", "QRP Severity",
                "Participant variance", "Vignette variance", "Residual variance",
                "ICC: Participant", "ICC: Vignette",
                "AIC", "BIC"),
  b = c(
    as.character(fe_ft1$b["(Intercept)"]),
    as.character(fe_ft1$b["severity_num"]),
    ifelse("responseid" %in% names(re_ft1), as.character(re_ft1["responseid"]), "—"),
    ifelse("severity"   %in% names(re_ft1), as.character(re_ft1["severity"]),   "—"),
    ifelse("Residual"   %in% names(re_ft1), as.character(re_ft1["Residual"]),   "—"),
    ifelse("responseid" %in% names(icc_ft1), as.character(icc_ft1["responseid"]), "—"),
    ifelse("severity"   %in% names(icc_ft1), as.character(icc_ft1["severity"]),   "—"),
    as.character(round(AIC(FT1), 1)),
    as.character(round(BIC(FT1), 1))
  ),
  SE = c(
    as.character(fe_ft1$se["(Intercept)"]),
    as.character(fe_ft1$se["severity_num"]),
    "", "", "", "", "", "", ""
  ),
  p = c(
    fmt_p(fe_ft1$p["(Intercept)"]),
    fmt_p(fe_ft1$p["severity_num"]),
    "", "", "", "", "", "", ""
  ),
  stringsAsFactors = FALSE
) %>%
  kable(caption = "Table 3. MLM Results for Perceived Trueness of Finding (FT1)",
        col.names = c("Parameter", "b", "SE", "p"),
        align = c("l", "r", "r", "r")) %>%
  kable_styling(full_width = FALSE, font_size = 11,
                bootstrap_options = c("condensed", "bordered")) %>%
  footnote(general = "Trueness centered at 3 (neutral). QRP Severity: minor = −1, moderate = 0, major = 1. * p < .05. ** p < .01. *** p < .001.",
           general_title = "Note.", footnote_as_chunk = TRUE)
```

