---
title: "Diss cleaning"
author: "SCL"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

```{r}
# -------------------------
# d -> eta2 -> f2 and participant counts (design-effect method)
# -------------------------
# install packages if needed
if (!requireNamespace("pwr", quietly = TRUE)) install.packages("pwr")
if (!requireNamespace("sjstats", quietly = TRUE)) install.packages("sjstats")

library(pwr)      # pwr.f2.test
library(sjstats)  # design_effect
library(dplyr)
library(tibble)
library(purrr)
library(tidyverse)
library(janitor)
library(here)
library(psych)
library(car)
library(effectsize)
library(broom)
library(knitr)
library(kableExtra)
library(lattice)
library(nlme)
library(lubridate)
library(lme4)
library(lmerTest)
```

LOAD DATA

```{r data-load}
library(here)
data_path <- here::here("Diss_full.csv")
diss.full <- read.csv(data_path)
```

LET'S START CLEANING

```{r}
#make all the columns lowercase to help with coding 
names(diss.full) =tolower(names(diss.full))
names(diss.full) <- iconv(names(diss.full), from = "", to = "UTF-8", sub = "")
names(diss.full) <- gsub("consent.*", "consent", names(diss.full))

```

```{r}
# Initial data count
initial_count <- nrow(diss.full)
print(initial_count)

# Clean recordeddate
diss.full$recordeddate <- str_squish(as.character(diss.full$recordeddate))

# Parse date-only column
diss.full$created_date = mdy_hm(diss.full$recordeddate)

# Filter by cutoff date
cutoff_date <- as.Date("2026-01-27")
filtered_by_date <- diss.full %>%
  filter(!is.na(created_date) & created_date >= cutoff_date)

count_by_date <- nrow(filtered_by_date)
print(count_by_date)

# Filter by consent
filtered_by_consent = filtered_by_date %>%
  filter(consent == "Yes, I consent")

count_by_consent <- nrow(filtered_by_consent)

# Filter by duration (exclude under 420 seconds)
filtered_by_duration <- filtered_by_consent %>%
  filter(!is.na(duration..in.seconds.) & duration..in.seconds. >= 420)

count_by_duration <- nrow(filtered_by_duration)

# Exclude participants under 18
filtered_by_age <- filtered_by_duration %>%
  filter(is.na(age) | age >= 18)

count_by_age <- nrow(filtered_by_age)


# Exclude no-variability: participants who gave identical responses across
# all trust and likeability items — uses apply() to avoid rowwise() issues
trust_like_cols = c("khon","ksin","keth","klike","kapp",
                    "shon","ssin","seth","slike","sapp",
                    "hhon","hsin","heth","hlike","happ",
                    "fhon","fsin","feth","flike","fapp",
                    "xhon","xsin","xeth","xlike","xapp",
                    "yhon","ysin","yeth","ylike","yapp")

tl_matrix = filtered_by_age %>%
  select(all_of(trust_like_cols)) %>%
  mutate(across(everything(), as.numeric))

has_variability = apply(tl_matrix, 1, function(row) n_distinct(na.omit(row)) > 1)
filtered_by_variability = filtered_by_age[has_variability, ]
count_by_variability = nrow(filtered_by_variability)

# Exclude attention check failures (attention1 == 2 is correct response)
filtered_by_attention = filtered_by_variability %>%
  filter(attention1 == 2)
count_by_attention = nrow(filtered_by_attention)
# Final count
final_count <- nrow(filtered_by_age)

# Summary table
count_summary <- data.frame(
  Step = c(
    "Initial",
    "After Date Filter",
    "After Consent Filter",
    "After Duration Filter",
    "After Age Filter",
    "Final"
  ),
  Count = c(
    initial_count,
    count_by_date,
    count_by_consent,
    count_by_duration,
    count_by_age,
    final_count
  )
)

print(count_summary)

# Print counts
cat("Total rows in diss.full:", initial_count, "\n")
cat("Rows after filtering by date:", count_by_date, "\n")
cat("Rows after filtering by consent:", count_by_consent, "\n")
cat("Rows after filtering by duration:", count_by_duration, "\n")
cat("Rows after excluding participants under 18:", count_by_age, "\n")
cat("Final rows:", final_count, "\n")
```

```{r}
attr_dat <- filtered_by_age %>%
  select(
    responseid,
    minsmart, minbetter, mincreative, minrather, minshould, minregard, mintyp, minkeep, minget,
    modsmart, modbett, modcreat, modrath, modshou, modreg, modtyp, modkeep, modget,
    majsmart, majbet, majcreat, majrath, majshould, majreg, majtyp, majkeep, majget
  )
```

```{r}
attr_long <- attr_dat %>%
  pivot_longer(
    cols = -responseid,
    names_to = "raw_item",
    values_to = "choice_raw"
  )
```

```{r}
attr_long <- attr_long %>%
  mutate(
    severity = case_when(
      str_detect(raw_item, "^min") ~ "minor",
      str_detect(raw_item, "^mod") ~ "moderate",
      str_detect(raw_item, "^maj") ~ "major",
      TRUE ~ NA_character_
    ),
    item_stub = str_remove(raw_item, "^(min|mod|maj)"),
    attribute = case_when(
      item_stub %in% c("smart") ~ "smarter",
      item_stub %in% c("better", "bett") ~ "better_researcher",
      item_stub %in% c("creative", "creat") ~ "creative",
      item_stub %in% c("rather", "rath") ~ "rather_be",
      item_stub %in% c("should", "shou") ~ "should_be",
      item_stub %in% c("regard", "reg") ~ "celebrated",
      item_stub %in% c("typ") ~ "typical",
      item_stub %in% c("keep") ~ "job_security",
      item_stub %in% c("get") ~ "job_outcome",
      TRUE ~ NA_character_
    )
  )
```

```{r}
head(attr_long, 20)
table(attr_long$severity, useNA = "ifany")
table(attr_long$attribute, useNA = "ifany")
```

```{r}
attr_long2 <- attr_long %>%
  tidyr::crossing(researcher = c("investigator", "inspector"))
```

```{r}
head(attr_long2, 20)
dim(attr_long)
dim(attr_long2)
```

```{r}
attr_long2 <- attr_long2 %>%
  mutate(
    chosen = case_when(
      str_detect(choice_raw, "^reported researcher") & researcher == "investigator" ~ 1,
      str_detect(choice_raw, "^reporting researcher") & researcher == "inspector" ~ 1,
      str_detect(choice_raw, "^neither") ~ 0,
      TRUE ~ 0
    )
  )
```

```{r}
head(attr_long2, 20)
table(attr_long2$chosen, useNA = "ifany")
table(attr_long2$researcher, attr_long2$chosen)
```

```{r}
attr_model_dat <- attr_long2 %>%
  mutate(
    researcher_ec = if_else(researcher == "inspector", 1, -1),
    severity_num = case_when(
      severity == "minor" ~ -1,
      severity == "moderate" ~ 0,
      severity == "major" ~ 1
    ),
    responseid = factor(responseid),
    researcher = factor(researcher, levels = c("investigator", "inspector")),
    severity = factor(severity, levels = c("minor", "moderate", "major")),
    attribute = factor(
      attribute,
      levels = c(
        "smarter",
        "better_researcher",
        "creative",
        "rather_be",
        "should_be",
        "celebrated",
        "typical",
        "job_security",
        "job_outcome"
      )
    ),
    vignette_id = factor(severity)
  )
contrasts(attr_model_dat$attribute) <- contr.sum
```

```{r}
str(attr_model_dat)
table(attr_model_dat$researcher)
table(attr_model_dat$severity)
table(attr_model_dat$attribute)
table(attr_model_dat$researcher_ec)
table(attr_model_dat$severity_num)
```

```{r}
A1 <- glmer(
  chosen ~ researcher_ec + attribute +
    (1 | responseid) + (1 | vignette_id),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa")
)
```

```{r}
# extract the 8 printed attribute coefficients
coefs <- fixef(A1)
atts <- coefs[grep("^attribute", names(coefs))]

# compute the 9th (implied) coefficient
attribute9 <- -sum(atts)

# build the full vector with names
att_names <- levels(attr_model_dat$attribute)
full_att_coefs <- c(atts, attribute9)
names(full_att_coefs) <- att_names

# print it
full_att_coefs
```

```{r}
# chosen = 0 (not selected), 1 (selected)
summary(A1)
```

```{r}
# A2 tests whether choice differs by severity, controlling for attribute
# chosen = 0 (not selected), 1 (selected)

A2 <- glmer(
  chosen ~ attribute + severity_num +
    (1 | responseid),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(A2)
```

```{r}
# A3: Tests whether choice differs by BOTH researcher and severity,
# while controlling for attribute type

# DV: chosen (0 = not selected, 1 = selected)

A3 <- glmer(
  chosen ~ researcher_ec + attribute + severity_num +
    (1 | responseid),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(A3)
```

```{r}
# A4: Tests whether the effect of researcher depends on severity,
# while controlling for attribute type

# DV: chosen (0 = not selected, 1 = selected)

A4 <- glmer(
  chosen ~ researcher_ec * severity_num + attribute +
    (1 | responseid),
  data = attr_model_dat,
  family = binomial,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
)

summary(A4)
```

------------------------------------------------------------------------

# ============================================================

# TRUST & LIKEABILITY ANALYSIS (RQ1, RQ2) + TRUENESS (RQ3)

# ============================================================

## STEP 1: Build the long-format trust/likeability/trueness dataset

```{r build-trust-long}
# ── Vignette metadata ──────────────────────────────────────────────────────
# Each vignette pair: investigator (inv) and inspector (insp)
# Severity: minor = vignette K/S, moderate = H/F, major = X/Y
# Trust items   : hon, sin, eth  (honest, sincere, ethical)
# Likeability   : like, app      (likeable, approachable)
# Trueness (conf): investigator only, 1 item per vignette

vignette_map = list(
  list(vig_id = "minor",    role = "investigator",
       hon = "khon", sin = "ksin",  eth = "keth",
       like = "klike",  app = "kapp",  conf = "kcon"),
  list(vig_id = "minor",    role = "inspector",
       hon = "shon",    sin = "ssin",  eth = "seth",
       like = "slike",  app = "sapp",  conf = NA),
  list(vig_id = "moderate", role = "investigator",
       hon = "hhon",    sin = "hsin",  eth = "heth",
       like = "hlike",  app = "happ",  conf = "hcon"),
  list(vig_id = "moderate", role = "inspector",
       hon = "fhon",    sin = "fsin",  eth = "feth",
       like = "flike",  app = "fapp",  conf = NA),
  list(vig_id = "major",    role = "investigator",
       hon = "xhon",   sin = "xsin",  eth = "xeth",
       like = "xlike",  app = "xapp",  conf = "xcon"),
  list(vig_id = "major",    role = "inspector",
       hon = "yhon",    sin = "ysin",  eth = "yeth",
       like = "ylike",  app = "yapp",  conf = NA)
)

# ── Helper: extract numeric value from labelled string ─────────────────────
parse_num = function(x) as.numeric(str_extract(as.character(x), "^\\d"))

# ── Build one row per participant × vignette × role ──────────────────────
tl_rows = map_dfr(vignette_map, function(v) {
  filtered_by_age %>%                          # use cleaned dataset
    transmute(
      responseid,
      vig_id   = v$vig_id,
      role     = v$role,
      hon_raw  = parse_num(.data[[v$hon]]),
      sin_raw  = parse_num(.data[[v$sin]]),
      eth_raw  = parse_num(.data[[v$eth]]),
      like_raw = parse_num(.data[[v$like]]),
      app_raw  = parse_num(.data[[v$app]]),
      conf_raw = if (!is.na(v$conf)) parse_num(.data[[v$conf]]) else NA_real_
    )
})

# ── Composites & factors ───────────────────────────────────────────────────
tl_dat = tl_rows %>%
  mutate(
    trust      = rowMeans(cbind(hon_raw, sin_raw, eth_raw), na.rm = TRUE),
    likeability = rowMeans(cbind(like_raw, app_raw), na.rm = TRUE),
    severity   = factor(vig_id,   levels = c("minor", "moderate", "major")),
    role       = factor(role,     levels = c("investigator", "inspector")),
    responseid = factor(responseid),
    # effect-coded predictors
    role_ec    = if_else(role == "inspector", 1, -1),
    severity_num = case_when(
      severity == "minor"    ~ -1,
      severity == "moderate" ~  0,
      severity == "major"    ~  1
    )
  )

glimpse(tl_dat)
```

Check structure and counts

```{r tl-checks}
table(tl_dat$role, tl_dat$severity)

# Quick descriptives
tl_dat %>%
  group_by(role, severity) %>%
  summarise(
    n          = sum(!is.na(trust)),
    trust_M    = round(mean(trust, na.rm = TRUE), 2),
    trust_SD   = round(sd(trust,   na.rm = TRUE), 2),
    like_M     = round(mean(likeability, na.rm = TRUE), 2),
    like_SD    = round(sd(likeability,   na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  kable(caption = "Descriptives: Trust & Likeability by Role × Severity") %>%
  kable_styling()
```

------------------------------------------------------------------------

## STEP 2: Reliability & validation checks

```{r reliability}
library(psych)

# ── Trust alpha per role × severity (using the 3 items) ───────────────────
trust_items_inv = filtered_by_age %>%
  transmute(
    min_hon = parse_num(khon), min_sin = parse_num(ksin),   min_eth = parse_num(keth),
    mod_hon = parse_num(hhon),    mod_sin = parse_num(hsin),   mod_eth = parse_num(heth),
    maj_hon = parse_num(xhon),   maj_sin = parse_num(xsin),   maj_eth = parse_num(xeth)
  )

trust_items_insp = filtered_by_age %>%
  transmute(
    min_hon = parse_num(shon),  min_sin = parse_num(ssin),  min_eth = parse_num(seth),
    mod_hon = parse_num(fhon),  mod_sin = parse_num(fsin),  mod_eth = parse_num(feth),
    maj_hon = parse_num(yhon),  maj_sin = parse_num(ysin),  maj_eth = parse_num(yeth)
  )

psych::alpha(trust_items_inv,  check.keys = TRUE)$total %>% select(raw_alpha, std.alpha) %>% print()

psych::alpha(trust_items_insp, check.keys = TRUE)$total %>% select(raw_alpha, std.alpha) %>% print()

# ── Likeability alpha ──────────────────────────────────────────────────────
like_items_inv = filtered_by_age %>%
  transmute(
    min_like = parse_num(klike), min_app = parse_num(kapp),
    mod_like = parse_num(hlike), mod_app = parse_num(happ),
    maj_like = parse_num(xlike), maj_app = parse_num(xapp)
  )

like_items_insp = filtered_by_age %>%
  transmute(
    min_like = parse_num(slike), min_app = parse_num(sapp),
    mod_like = parse_num(flike), mod_app = parse_num(fapp),
    maj_like = parse_num(ylike), maj_app = parse_num(yapp)
  )

psych::alpha(like_items_inv,  check.keys = TRUE)$total %>% select(raw_alpha, std.alpha) %>% print()

psych::alpha(like_items_insp, check.keys = TRUE)$total %>% select(raw_alpha, std.alpha) %>% print()

# ── Inter-composite correlation ────────────────────────────────────────────
cor.test(tl_dat$trust, tl_dat$likeability, use = "complete.obs") %>% tidy() %>% print()
```

------------------------------------------------------------------------

## STEP 3: Null models (Model 0) — ICC partitioning

```{r null-models}
library(lme4)
library(lmerTest)

# ── Trust null model ───────────────────────────────────────────────────────
M0_trust = lmer(
  trust ~ 1 + (1 | responseid) + (1 | severity),
  data = tl_dat,
  REML = TRUE
)
summary(M0_trust)

# ICC: proportion of variance at each level
vc_trust = as.data.frame(VarCorr(M0_trust))
icc_participant_trust = vc_trust$vcov[vc_trust$grp == "responseid"] / sum(vc_trust$vcov)
icc_vignette_trust    = vc_trust$vcov[vc_trust$grp == "severity"]   / sum(vc_trust$vcov)

print(paste("Trust ICC (participant):", round(icc_participant_trust, 3)))
print(paste("Trust ICC (vignette):",    round(icc_vignette_trust, 3)))

# ── Likeability null model ─────────────────────────────────────────────────
M0_like = lmer(
  likeability ~ 1 + (1 | responseid) + (1 | severity),
  data = tl_dat,
  REML = TRUE
)
summary(M0_like)

vc_like = as.data.frame(VarCorr(M0_like))
icc_participant_like = vc_like$vcov[vc_like$grp == "responseid"] / sum(vc_like$vcov)
icc_vignette_like    = vc_like$vcov[vc_like$grp == "severity"]   / sum(vc_like$vcov)

print(paste("Likeability ICC (participant):", round(icc_participant_like, 3)))
print(paste("Likeability ICC (vignette):",    round(icc_vignette_like, 3)))
```

------------------------------------------------------------------------

## STEP 4: RQ1 — Trust models (H1a: main effect of role; H1b: role × severity)

```{r trust-models}
# Model 1: Role only (H1a)
T1 = lmer(
  trust ~ role_ec + (1 | responseid) + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 2: Severity only
T2 = lmer(
  trust ~ severity_num + (1 | responseid) + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 3: Role + Severity (additive)
T3 = lmer(
  trust ~ role_ec + severity_num + (1 | responseid) + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 4: Role × Severity interaction (H1b)
T4 = lmer(
  trust ~ role_ec * severity_num + (1 | responseid) + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# ── Model comparison ───────────────────────────────────────────────────────
anova(T1, T2, T3, T4)

# ── Summaries ─────────────────────────────────────────────────────────────
summary(T1)
summary(T3)
summary(T4)
```

Planned contrasts: inspectors vs investigators at each severity level (Bonferroni α = .001)

```{r trust-contrasts}
library(emmeans)

emm_trust = emmeans(T4, ~ role_ec | severity_num,
                     at = list(severity_num = c(-1, 0, 1)))

# Recode for readable output
emm_trust_role = emmeans(T4, pairwise ~ role_ec | severity_num,
                           at = list(severity_num = c(-1, 0, 1)),
                           adjust = "bonferroni")
summary(emm_trust_role$contrasts)

# Effect sizes (Cohen's d)
eff_size(emm_trust, sigma = sigma(T4), edf = df.residual(T4))
```

Plot Role × Severity for trust

```{r trust-plot}
emm_trust_df = as.data.frame(emmeans(T4, ~ role_ec * severity_num,
                                       at = list(severity_num = c(-1, 0, 1))))
emm_trust_df = emm_trust_df %>%
  mutate(
    Role     = if_else(role_ec == 1, "Inspector", "Investigator"),
    Severity = factor(severity_num, levels = c(-1, 0, 1),
                      labels = c("Minor", "Moderate", "Major"))
  )

ggplot(emm_trust_df, aes(x = Severity, y = emmean, color = Role, group = Role)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.15) +
  scale_color_manual(values = c("Inspector" = "#2196F3", "Investigator" = "#E53935")) +
  labs(title = "Estimated Trust by Role and QRP Severity",
       y = "Estimated Marginal Mean (Trust)", x = "QRP Severity") +
  theme_minimal(base_size = 13) +
  coord_cartesian(ylim = c(1, 5))
```

------------------------------------------------------------------------

## STEP 5: RQ2 — Likeability models (H2a: main effect of role; H2b: role × severity)

```{r likeability-models}
# Model 1: Role only (H2a)
L1 = lmer(
  likeability ~ role_ec + (1 | responseid) + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 2: Severity only
L2 = lmer(
  likeability ~ severity_num + (1 | responseid) + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 3: Role + Severity (additive)
L3 = lmer(
  likeability ~ role_ec + severity_num + (1 | responseid) + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Model 4: Role × Severity interaction (H2b)
L4 = lmer(
  likeability ~ role_ec * severity_num + (1 | responseid) + (1 | severity),
  data = tl_dat, REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# ── Model comparison ───────────────────────────────────────────────────────
anova(L1, L2, L3, L4)

summary(L1)
summary(L3)
summary(L4)
```

Planned contrasts: Bonferroni α = .001

```{r likeability-contrasts}
emm_like_role = emmeans(L4, pairwise ~ role_ec | severity_num,
                          at = list(severity_num = c(-1, 0, 1)),
                          adjust = "bonferroni")
summary(emm_like_role$contrasts)

eff_size(emmeans(L4, ~ role_ec | severity_num,
                  at = list(severity_num = c(-1, 0, 1))),
         sigma = sigma(L4), edf = df.residual(L4))
```

Plot Role × Severity for likeability

```{r like-plot}
emm_like_df = as.data.frame(emmeans(L4, ~ role_ec * severity_num,
                                      at = list(severity_num = c(-1, 0, 1)))) %>%
  mutate(
    Role     = if_else(role_ec == 1, "Inspector", "Investigator"),
    Severity = factor(severity_num, levels = c(-1, 0, 1),
                      labels = c("Minor", "Moderate", "Major"))
  )

ggplot(emm_like_df, aes(x = Severity, y = emmean, color = Role, group = Role)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.15) +
  scale_color_manual(values = c("Inspector" = "#2196F3", "Investigator" = "#E53935")) +
  labs(title = "Estimated Likeability by Role and QRP Severity",
       y = "Estimated Marginal Mean (Likeability)", x = "QRP Severity") +
  theme_minimal(base_size = 13) +
  coord_cartesian(ylim = c(1, 5))
```

------------------------------------------------------------------------
```{r}
# Refit model using RAW trueness (not centered)
FT1_raw <- lmer(
  trueness ~ severity_num + (1 | responseid) + (1 | severity),
  data    = trueness_dat,
  REML    = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Estimated marginal means on the original 1–5 scale
emm_true_df_raw <- as.data.frame(
  emmeans(FT1_raw, ~ severity_num,
          at = list(severity_num = c(-1, 0, 1)))
) %>%
  mutate(
    Severity = factor(
      severity_num,
      levels = c(-1, 0, 1),
      labels = c("Minor", "Moderate", "Major")
    )
  )

# Plot on the 1–5 scale
ggplot(emm_true_df_raw, aes(x = Severity, y = emmean, group = 1)) +
  geom_line(linewidth = 1, color = "#7B1FA2") +
  geom_point(size = 3, color = "#7B1FA2") +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL),
                width = 0.15, color = "#7B1FA2") +
  labs(
    title = "Perceived Trueness of Finding by QRP Severity",
    y = "Estimated Marginal Mean (Trueness)",
    x = "QRP Severity"
  ) +
  theme_minimal(base_size = 13) +
  coord_cartesian(ylim = c(1, 5))

```

## STEP 6: RQ3 — Perceived Trueness of the Finding (H3: severity → trueness)

```{r trueness-data}
# Trueness is only for investigators, one item per vignette
trueness_dat = filtered_by_age %>%
  transmute(
    responseid,
    minor    = parse_num(kcon),
    moderate = parse_num(hcon),
    major    = parse_num(xcon)
  ) %>%
  pivot_longer(
    cols      = c(minor, moderate, major),
    names_to  = "severity",
    values_to = "trueness"
  ) %>%
  mutate(
    severity     = factor(severity, levels = c("minor", "moderate", "major")),
    severity_num = case_when(
      severity == "minor"    ~ -1,
      severity == "moderate" ~  0,
      severity == "major"    ~  1
    ),
    responseid = factor(responseid),
    trueness_c = trueness - 3
  )

# Descriptives
trueness_dat %>%
  group_by(severity) %>%
  summarise(
    n  = sum(!is.na(trueness)),
    M  = round(mean(trueness, na.rm = TRUE), 2),
    SD = round(sd(trueness,   na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  kable(caption = "Trueness Descriptives by QRP Severity") %>%
  kable_styling()
```

Model FT1: Trueness \~ Severity (H3)

```{r trueness-model}
FT1 = lmer(
  trueness_c ~ severity_num + (1 | responseid) + (1 | severity),
  data    = trueness_dat,
  REML    = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(FT1)

# Planned contrasts across severity levels
emm_trueness = emmeans(FT1, pairwise ~ severity_num,
                         at     = list(severity_num = c(-1, 0, 1)),
                         adjust = "bonferroni")
summary(emm_trueness$contrasts)

eff_size(emmeans(FT1, ~ severity_num, at = list(severity_num = c(-1, 0, 1))),
         sigma = sigma(FT1), edf = df.residual(FT1))
```

Plot trueness by severity

```{r trueness-plot}
emm_true_df = as.data.frame(
  emmeans(FT1, ~ severity_num, at = list(severity_num = c(-1, 0, 1)))
) %>%
  mutate(Severity = factor(severity_num, levels = c(-1, 0, 1),
                            labels = c("Minor", "Moderate", "Major")))

ggplot(emm_true_df, aes(x = Severity, y = emmean, group = 1)) +
  geom_line(linewidth = 1, color = "#7B1FA2") +
  geom_point(size = 3, color = "#7B1FA2") +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.15,
                color = "#7B1FA2") +
  labs(title = "Perceived Trueness of Finding by QRP Severity",
       y = "Estimated Marginal Mean (Trueness)", x = "QRP Severity") +
  theme_minimal(base_size = 13) +
  coord_cartesian()

```

------------------------------------------------------------------------
```{r}

```

## STEP 7: Robustness checks — demographic covariates

```{r robustness-demographics}
# Attach demographics to tl_dat
demo_dat = filtered_by_age %>%
  transmute(
    responseid = responseid,
    gender     = factor(`gender.identity`),
    political  = factor(political, levels = c(
      "Strongly Liberal", "Liberal", "Lean Liberal",
      "Centrist",
      "Lean Conservative", "Conservative", "Strongly Conservative"
    )),
    religion   = factor(religion)
  )

tl_robust = tl_dat %>%
  mutate(responseid = as.character(responseid)) %>%
  left_join(demo_dat, by = "responseid") %>%
  mutate(responseid = factor(responseid))


# Trust robustness model (Model 4 + demographics)
T4_robust = lmer(
  trust ~ role_ec * severity_num + gender + political + religion +
    (1 | responseid) + (1 | severity),
  data    = tl_robust,
  REML    = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

L4_robust = lmer(
  likeability ~ role_ec * severity_num + gender + political + religion +
    (1 | responseid) + (1 | severity),
  data    = tl_robust,
  REML    = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)


summary(L4_robust)

# Compare role_ec * severity_num effect with and without demographics
summary(T4_robust)
summary(L4_robust)

# Check if the interaction term stays significant in both
fixef(T4)[["role_ec:severity_num"]]
fixef(T4_robust)[["role_ec:severity_num"]]

fixef(L4)[["role_ec:severity_num"]]
fixef(L4_robust)[["role_ec:severity_num"]]
```
```{r}
tl_robust$ideology_num <- as.numeric(tl_robust$political)

# Center it for interpretation
tl_robust$ideology_c <- scale(tl_robust$ideology_num, scale = FALSE)

```

```{r}
trust_mod_ideo <- lmer(
  trust ~ role_ec * severity_num * ideology_c +
    gender + political + religion +
    (1 | responseid) + (1 | severity),
  data = tl_robust,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(trust_mod_ideo)

```

```{r}
tl_robust$ideology_num <- as.numeric(tl_robust$political)
tl_robust$ideology_c <- scale(tl_robust$ideology_num, scale = FALSE)


```

```{r}
trust_mod_pol <- lmer(
  trust ~ role_ec * severity_num * ideology_c +
    (1 | responseid) + (1 | severity),
  data = tl_robust,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(trust_mod_pol)

```


```{r}
trust_mod_pol2 <- lmer(
  trust ~ role_ec * severity_num * ideology_c +
    gender + religion +
    (1 | responseid) + (1 | severity),
  data = tl_robust,
  REML = FALSE
)
summary(trust_mod_pol2)
```

```{r}
like_mod_ideo <- lmer(
  likeability ~ role_ec * severity_num * ideology_c +
    gender + religion +
    (1 | responseid) + (1 | severity),
  data = tl_robust,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(like_mod_ideo)

```


